### 2014-11-13 conclusions.tex
Fix more typos.
small changes. eliminated last paragraph.

We have presented a novel way of adding coordination to a declarative language without
changing the nature of the language or introducing non-declarative constructs. We
took advantage of the fact that CLM uses linear logic, which allows us to derive
coordination facts that can be deleted in order to perform actions in the underlying
runtime system. In the other hand, sensing facts allow the programmer to reason
about data locality and scheduling of computation in a data-driven fashion.
Even though the programs are optimized, programs remain declarative and proving
interesting properties of the programs remains simple because it is possible to
reason about the logical rules that drive coordination.

We would like to explore CLM's coordination principles in distributed systems,
where data locality is far more important than in shared memory systems.
Furthermore, we think that other declarative paradigms such as functional
programming would benefit from giving programmers the freedom to fine-tune their
programs.

>>>>

We have presented a novel way of adding coordination to a declarative
language without changing the nature of the language or introducing
non-declarative constructs. We took advantage of the fact that CLM
uses linear logic, which allows us to derive coordination facts that
can be deleted in order to perform actions in the underlying runtime
system. Sensing facts allow the programmer to reason about data
locality and scheduling of computation in a data-driven fashion.
Action can then be used to affect how the program runs on the
underlying system.  The resulting programs perform well and yet the
programs remain declarative and proving interesting properties of the
programs remains simple because it is possible to reason about the
logical rules that drive both the computation and coordination.

\iffalse
We would like to explore CLM's coordination principles in distributed
systems, where data locality is far more important than in shared
memory systems.  Furthermore, we think that other declarative
paradigms such as functional programming would benefit from giving
programmers the freedom to fine-tune their programs.
\fi
